A Note on Convergence Diagnostics for Multiple Imputation using Chained Equations (MICE)

### 2019-11-29 Simulation/Writeup/NoteConvergence.Rnw
Remarks meeting with Gerko on overcoverage
Adjust table with results

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Sun Nov 24 19:18:40 2019
\begin{table}[ht]
\centering
\caption{Simulation and convergence diagnostics over 1000 MCMC simulations.} 
\label{results}
\begin{tabular}{lrrrrrrrr}
  \hline
 & Bias & Emp.SE & CI.width & Cov.rate & R.hat & R.var & Autocorr & AC.var \\ 
  \hline
1 & -0.279 & 0.072 & 0.905 & 0.851 & \textsuperscript{a} & \textsuperscript{a} & \textsuperscript{a} & \textsuperscript{a} \\ 
  2 & -0.171 & 0.070 & 0.924 & 0.947 & 1.665 & 1.635 & -0.500 & -0.500 \\ 
  3 & -0.162 & 0.068 & 0.901 & 0.954 & 1.322 & 1.306 & -0.660 & -0.660 \\ 
  4 & -0.158 & 0.072 & 0.899 & 0.961 & 1.459 & 1.449 & -0.738 & -0.737 \\ 
  5 & -0.162 & 0.071 & 0.907 & 0.951 & 1.469 & 1.471 & -0.706 & -0.706 \\ 
  6 & -0.160 & 0.072 & 0.910 & 0.962 & 1.252 & 1.256 & -0.652 & -0.658 \\ 
  7 & -0.160 & 0.072 & 0.921 & 0.967 & 1.265 & 1.259 & -0.572 & -0.582 \\ 
  8 & -0.158 & 0.069 & 0.914 & 0.963 & 1.181 & 1.178 & -0.496 & -0.510 \\ 
  9 & -0.162 & 0.072 & 0.923 & 0.963 & 1.188 & 1.182 & -0.434 & -0.472 \\ 
  10 & -0.161 & 0.072 & 0.911 & 0.968 & 1.139 & 1.138 & -0.396 & -0.452 \\ 
  15 & -0.161 & 0.073 & 0.923 & 0.960 & 1.097 & 1.101 & -0.273 & -0.301 \\ 
  20 & -0.158 & 0.070 & 0.916 & 0.971 & 1.067 & 1.066 & -0.187 & -0.212 \\ 
  25 & -0.159 & 0.071 & 0.885 & 0.961 & 1.056 & 1.055 & -0.122 & -0.166 \\ 
  50 & -0.159 & 0.070 & 0.906 & 0.950 & 1.026 & 1.026 & -0.032 & -0.071 \\ 
  100 & -0.157 & 0.069 & 0.921 & 0.973 & 1.013 & 1.013 & 0.012 & -0.013 \\ 
   \hline %{\footnotesize{Note: \textsuperscript{a}  signifies that no convergence diagnostic could be computed.}
\end{tabular}
\end{table}

From \textsuperscript{a} the simulation diagnostics it appears that as little as three iterations is sufficient to draw valid inference. Convergence diagnostics $\widehat{R}$ and auto-correlation, however, indicate 20-30 iterations. Apparently, they are not perfect for MI data [move interpretation to Discussion!].

>>>>

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Nov 29 11:38:27 2019
\begin{table}[ht]
\centering
\caption{Simulation and convergence diagnostics over 1000 MCMC simulations.} 
\label{results}
\begin{tabular}{lrrrrrrr}
  \hline
It. & Bias & CI width & Cov. rate & $\widehat{R}$ & $\widehat{R}$ & Auto-corr. & Auto-corr. \\ 
  \hline
   1 & -0.128 & 0.922 & 0.930 & NA & NA & NA & NA \\ 
     2 & -0.002 & 0.915 & 0.940 & 1.686 & 1.709 & -0.500 & -0.500 \\ 
     3 & 0.012 & 0.923 & 0.960 & 1.317 & 1.326 & -0.661 & -0.659 \\ 
     4 & 0.019 & 0.892 & 0.970 & 1.461 & 1.464 & -0.735 & -0.746 \\ 
     5 & 0.015 & 0.906 & 0.910 & 1.486 & 1.472 & -0.706 & -0.705 \\ 
     6 & 0.010 & 0.928 & 0.950 & 1.252 & 1.261 & -0.651 & -0.667 \\ 
     7 & 0.006 & 0.908 & 0.910 & 1.259 & 1.267 & -0.619 & -0.584 \\ 
     8 & 0.018 & 0.920 & 0.940 & 1.178 & 1.181 & -0.516 & -0.549 \\ 
     9 & 0.011 & 0.994 & 0.940 & 1.190 & 1.186 & -0.506 & -0.488 \\ 
    10 & 0.020 & 0.940 & 0.900 & 1.142 & 1.145 & -0.448 & -0.420 \\ 
    15 & 0.009 & 0.917 & 0.960 & 1.098 & 1.109 & -0.256 & -0.289 \\ 
    20 & 0.020 & 0.848 & 0.930 & 1.069 & 1.065 & -0.179 & -0.214 \\ 
    25 & 0.026 & 0.897 & 0.970 & 1.054 & 1.054 & -0.146 & -0.131 \\ 
    50 & 0.008 & 0.946 & 0.970 & 1.026 & 1.026 & -0.029 & -0.096 \\ 
   100 & 0.011 & 0.967 & 0.930 & 1.013 & 1.013 & 0.054 & -0.020 \\ 
   \hline
\end{tabular}
\end{table}

From the simulation diagnostics it appears that as little as three iterations is sufficient to draw valid inference. Convergence diagnostics $\widehat{R}$ and auto-correlation, however, indicate 20-30 iterations. Apparently, they are not perfect for MI data [move interpretation to Discussion!].

### 2019-11-29 Simulation/Writeup/NoteConvergence.tex
Remarks meeting with Gerko on overcoverage
Adjust table with results

% % latex table generated in R 3.6.1 by xtable 1.8-4 package
% % Tue Nov 12 17:43:11 2019
% \begin{table}[ht]
% \centering
% \begin{tabular}{lrrrrrrr}
%   \hline
%   &\multicolumn{4}{c}{Simulation Diagnostics}& & \multicolumn{2}{c}{Convergence Diagn.} \\
%   \cline{2-5} \cline{7-8}
% It. & Bias & Emp. SE & CI width & Cov. rate & & $\widehat{R}$ & Auto-corr. \\ 
%   \hline
% ...
% \end{tabular}
% \caption{Simulation and convergence diagnostics over 1000 MCMC simulations.}
% \label{subsetresults}
% \end{table}

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Sun Nov 24 19:18:40 2019
\begin{table}[ht]
\centering
\caption{Simulation and convergence diagnostics over 1000 MCMC simulations.} 
\label{results}
\begin{tabular}{lrrrrrrrr}
  \hline
 & Bias & Emp.SE & CI.width & Cov.rate & R.hat & R.var & Autocorr & AC.var \\ 
  \hline
1 & -0.279 & 0.072 & 0.905 & 0.851 & \textsuperscript{a} & \textsuperscript{a} & \textsuperscript{a} & \textsuperscript{a} \\ 
  2 & -0.171 & 0.070 & 0.924 & 0.947 & 1.665 & 1.635 & -0.500 & -0.500 \\ 
  3 & -0.162 & 0.068 & 0.901 & 0.954 & 1.322 & 1.306 & -0.660 & -0.660 \\ 
  4 & -0.158 & 0.072 & 0.899 & 0.961 & 1.459 & 1.449 & -0.738 & -0.737 \\ 
  5 & -0.162 & 0.071 & 0.907 & 0.951 & 1.469 & 1.471 & -0.706 & -0.706 \\ 
  6 & -0.160 & 0.072 & 0.910 & 0.962 & 1.252 & 1.256 & -0.652 & -0.658 \\ 
  7 & -0.160 & 0.072 & 0.921 & 0.967 & 1.265 & 1.259 & -0.572 & -0.582 \\ 
  8 & -0.158 & 0.069 & 0.914 & 0.963 & 1.181 & 1.178 & -0.496 & -0.510 \\ 
  9 & -0.162 & 0.072 & 0.923 & 0.963 & 1.188 & 1.182 & -0.434 & -0.472 \\ 
  10 & -0.161 & 0.072 & 0.911 & 0.968 & 1.139 & 1.138 & -0.396 & -0.452 \\ 
  15 & -0.161 & 0.073 & 0.923 & 0.960 & 1.097 & 1.101 & -0.273 & -0.301 \\ 
  20 & -0.158 & 0.070 & 0.916 & 0.971 & 1.067 & 1.066 & -0.187 & -0.212 \\ 
  25 & -0.159 & 0.071 & 0.885 & 0.961 & 1.056 & 1.055 & -0.122 & -0.166 \\ 
  50 & -0.159 & 0.070 & 0.906 & 0.950 & 1.026 & 1.026 & -0.032 & -0.071 \\ 
  100 & -0.157 & 0.069 & 0.921 & 0.973 & 1.013 & 1.013 & 0.012 & -0.013 \\ 
   \hline %{\footnotesize{Note: \textsuperscript{a}  signifies that no convergence diagnostic could be computed.}
\end{tabular}
\end{table}

From \textsuperscript{a} the simulation diagnostics it appears that as little as three iterations is sufficient to draw valid inference. Convergence diagnostics $\widehat{R}$ and auto-correlation, however, indicate 20-30 iterations. Apparently, they are not perfect for MI data [move interpretation to Discussion!].

>>>>

% latex table generated in R 3.6.1 by xtable 1.8-4 package
% Fri Nov 29 11:38:27 2019
\begin{table}[ht]
\centering
\caption{Simulation and convergence diagnostics over 1000 MCMC simulations.} 
\label{results}
\begin{tabular}{lrrrrrrr}
  \hline
It. & Bias & CI width & Cov. rate & $\widehat{R}$ & $\widehat{R}$ & Auto-corr. & Auto-corr. \\ 
  \hline
   1 & -0.128 & 0.922 & 0.930 & NA & NA & NA & NA \\ 
     2 & -0.002 & 0.915 & 0.940 & 1.686 & 1.709 & -0.500 & -0.500 \\ 
     3 & 0.012 & 0.923 & 0.960 & 1.317 & 1.326 & -0.661 & -0.659 \\ 
     4 & 0.019 & 0.892 & 0.970 & 1.461 & 1.464 & -0.735 & -0.746 \\ 
     5 & 0.015 & 0.906 & 0.910 & 1.486 & 1.472 & -0.706 & -0.705 \\ 
     6 & 0.010 & 0.928 & 0.950 & 1.252 & 1.261 & -0.651 & -0.667 \\ 
     7 & 0.006 & 0.908 & 0.910 & 1.259 & 1.267 & -0.619 & -0.584 \\ 
     8 & 0.018 & 0.920 & 0.940 & 1.178 & 1.181 & -0.516 & -0.549 \\ 
     9 & 0.011 & 0.994 & 0.940 & 1.190 & 1.186 & -0.506 & -0.488 \\ 
    10 & 0.020 & 0.940 & 0.900 & 1.142 & 1.145 & -0.448 & -0.420 \\ 
    15 & 0.009 & 0.917 & 0.960 & 1.098 & 1.109 & -0.256 & -0.289 \\ 
    20 & 0.020 & 0.848 & 0.930 & 1.069 & 1.065 & -0.179 & -0.214 \\ 
    25 & 0.026 & 0.897 & 0.970 & 1.054 & 1.054 & -0.146 & -0.131 \\ 
    50 & 0.008 & 0.946 & 0.970 & 1.026 & 1.026 & -0.029 & -0.096 \\ 
   100 & 0.011 & 0.967 & 0.930 & 1.013 & 1.013 & 0.054 & -0.020 \\ 
   \hline
\end{tabular}
\end{table}

From the simulation diagnostics it appears that as little as three iterations is sufficient to draw valid inference. Convergence diagnostics $\widehat{R}$ and auto-correlation, however, indicate 20-30 iterations. Apparently, they are not perfect for MI data [move interpretation to Discussion!].
